Respiratory Outbreak Trends in Toronto Healthcare Institutions Across the COVID-19 Pandemic 

### 2025-05-15 paper/paper.qmd
small fixes to code

---
title: "Respiratory Outbreak Trends in Toronto Healthcare Institutions Across the COVID-19 Pandemic "
subtitle: "The Response of Coronavirus and Other Respiratory Diseases to COVID-19 Pandemic Policies"
author: 
  - Evelyn Hughes
thanks: "Code and data are available at: [https://github.com/EveHughes/Donaldson-Paper]."
date: 05/12/2025
date-format: long

@@

#set up
import polars as pl
import matplotlib.pyplot as plt
pl.Config.set_tbl_hide_column_data_types(True)  
pl.Config(tbl_width_chars=1000)

#reading in of data & removing unneeded info
raw_data = pl.read_csv("../data/01-raw_data/ob_report_2019.csv")
for key in raw_data.columns:
  if key not in ["_id", "Type of Outbreak", "Causative Agent-1", "Causative Agent-2"]:
    raw_data = raw_data.drop(key)

@@

#rounding data
summary_data = summary_data.with_columns(sc.by_dtype(pl.Float64).round(2))

@@

#rounding all data
summary_data = summary_data.with_columns(sc.by_dtype(pl.Float64).round(2))

>>>>

---
title: "Respiratory Outbreak Trends in Toronto Healthcare Institutions Across the COVID-19 Pandemic "
subtitle: "The Response of Coronavirus and Other Respiratory Diseases to COVID-19 Pandemic Policies"
author: 
  - Evelyn Hughes
thanks: "Code and data are available at: https://github.com/EveHughes/Donaldson-Paper."
date: 05/12/2025
date-format: long

@@

#set up
import polars as pl
import matplotlib.pyplot as plt
from datetime import datetime

pl.Config.set_tbl_hide_column_data_types(True)  
pl.Config(tbl_width_chars=1000)

#reading in of data & removing unneeded info
date = str(datetime.today()).split()[0]

raw_data = pl.read_csv("../data/01-raw_data/" + date + "_ob_report_2019.csv")
for key in raw_data.columns:
  if key not in ["_id", "Type of Outbreak", "Causative Agent-1", "Causative Agent-2"]:
    raw_data = raw_data.drop(key)

@@

#rounding data
summary_data = summary_data.with_columns(sc.by_dtype(pl.Float64).cast(pl.Int64))

@@

#rounding all data & getting rid of quotes
summary_data = summary_data.with_columns(sc.by_dtype(pl.Float64).cast(pl.Int64))
